A Typed Programmatic Interface to Contracts on the Blockchain

### 2021-01-29 papers/execution-model/model.tex
Add files via upload
Some on the abstract (blue lines)

\begin{document}
\maketitle
\pagestyle{plain}
\begin{abstract}
  Integrating blockchain contracts in software systems requires a
  programmatic interface. We propose a typed interface for this
  purpose and establish some properties of the combined system. A
  prototype of the interface is implemented in OCaml for the Tezos
  blockchain. 
\end{abstract}

@@

\begin{lstlisting}[numbers=none]
while get-state(address).flag = true and bid < limit do
    bid = bid + a;
    call_contract(address, bid);
    Time.speep(5);
done;
\end{lstlisting}

>>>>

\begin{document}
\maketitle
\pagestyle{plain}
\begin{abstract} {\color{blue} Smart contract applications can reach their full potential if software programs can sufficiently interact with smart contracts on the blockchain.}
  Integrating blockchain contracts in software systems requires a
  programmatic interface. We propose a typed interface for this purpose and establish some properties of the combined system. {\color{blue} In detail, we provide an execution model that allows type-safe interaction between programs and the blockchain. Some designed properties are proven by the model.} A
  prototype of the interface is implemented in OCaml for the Tezos blockchain.  {\color{blue} The OCaml API allows user-programs to interact with an auction smart contract on the blockchain in a type-safe manner.}
\end{abstract}

@@

\begin{lstlisting}[numbers=none]
while get-state(address).flag = true and 
get-state(address).highestBid > bid and bid < limit do
    bid = bid + a;
    call_contract(address, bid); 
    Time.speep(5);
done;
\end{lstlisting}
